Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2012-03-05 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2012:03:05	14:46:57	(Mon 5.Mar)

\ifTODO
   \setlength{\marginparwidth}{1cm}
%    \setlength{\marginparpush}{1cm}
   \setlength\textwidth{\columnwidth}
   \addtolength\marginparsep{1.5cm}
   \definecolor{lightblue}{rgb}{0.8,0.8,1}
   \usepackage[backgroundcolor=LightBlue]{todonotes}
\else
   \usepackage[disable]{todonotes} 
\fi

@@

\IEEEPARstart{A}{daptive} beamformers have only recently been introduced in active sonar imaging.{\todo{break at something}} This is because , as demo file is intended to serve as a ``starter file''
for IEEE Computer Society journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.7 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

>>>>

\ifTODO
   \setlength{\marginparwidth}{1cm}
%    \setlength{\marginparpush}{1cm}
%    \setlength\marginpar{1.5cm}
   \addtolength\marginparsep{0.1cm}
%    \definecolor{lightblue}{rgb}{0.8,0.8,1}
%    \newlength\textwidthold
%    \setlength\textwidthold{\textwidth}
%    \setlength\textwidth{\columnwidth}
   \usepackage{./todonotes}
%    \setlength\textwidth\textwidthold
\else
   \usepackage[disable]{todonotes} 
\fi

@@

\IEEEPARstart{A}{daptive} beamformers have only recently been introduced in active sonar imaging.\todo{break at something} This is because , as demo file is intended to serve as a ``starter file''
for IEEE Computer Society journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.7 and later.

An attactive trait of the LCA is its low computational complexity; while the MV beamformer is of O($M^3$), the LCA method is of O($MW$), with $M$ being the number of channels and $W$ the number of windows. We made the LCA perform like the MV method using a well designed set of 30 windows. Hence, unless the array is very small, the proposed method will perform like the MV beamformer or better, and at a fraction of the computational cost.

An attactive trait of the LCA\todo{break at something} is its low computational complexity; while the MV beamformer is of O($M^3$), the LCA method is of O($MW$), with $M$ being the number of channels and $W$ the number of windows. We made the LCA perform like the MV method using a well designed set of 30 windows. Hence, unless the array is very small, the proposed method will perform like the MV beamformer or better, and at a fraction of the computational cost.

An attactive trait of the LCA is its low computational complexity; while the MV beamformer is of O($M^3$), the LCA method is of O($MW$), with $M$ being the number of channels and $W$ the number of windows. We made the LCA perform like the MV method using a well designed set of 30 windows. Hence, unless the array is very small, the proposed method will perform like the MV beamformer or better, and at a fraction of the computational cost.
